---
title: "Data Analysis"
execute: 
  warning: false
---

```{r}
#| message: false
#| echo: false

#| warning: false
library(tidyverse)
library(openair)
library(lubridate)
library(ggplot2)
library(dplyr)
library(lattice)
library(latticeExtra)

```

**The correlation of pm1 and pm2,5**

```{r}
#| message: false
#| echo: false

#| warning: false



data2 <- read_csv("sevan.csv")
data3 <- read_csv("ashotsk.csv")
data4 <- read_csv("azatan.csv")
data5 <- read_csv("gavar.csv")
data6 <- read_csv("maralik.csv")
data7 <- read_csv("panik.csv")
data8 <- read_csv("vazgen.csv")
data <- read_csv("artik.csv")
data_new <- data
data_new$year <- strftime(data_new$time, "%Y")
data_new$month <- strftime(data_new$time, "%m")
data_new$week <- strftime(data_new$time, "%w")
data |>
  ggplot(mapping = aes(x = pm2_5, y = pm1)) + geom_point(aes(col="state", size="popdensity")) + geom_smooth(method="loess", se=F)

```

**Description**

This plot shows that the numbers of pm1 and pm 2,5 are almost the same.

**The presence of temperature by time**

```{r}
#| message: false
#| echo: false

#| warning: false
ggplot() + geom_smooth(data_new, mapping = aes(x = time, y = temperature)) + geom_smooth(data2, mapping = aes(x = time, y = temperature)) + geom_smooth(data3, mapping = aes(x = time, y = temperature)) +geom_smooth(data4, mapping = aes(x = time, y = temperature)) + geom_smooth(data5, mapping = aes(x = time, y = temperature)) + geom_smooth(data6, mapping = aes(x = time, y = temperature)) + geom_smooth(data7, mapping = aes(x = time, y = temperature)) + geom_smooth(data8, mapping = aes(x = time, y = temperature), color = "orange")
```

```{}
```

**Description**

Thanks to this plot, we can compare temperatures in different cities in Armenia.

**The presence of pm1 by time**

```{r}

ggplot() + geom_smooth(data_new, mapping = aes(x = time, y = pm1)) + geom_smooth(data2, mapping = aes(x = time, y = pm1)) + geom_smooth(data3, mapping = aes(x = time, y = pm1)) +geom_smooth(data4, mapping = aes(x = time, y = pm1)) + geom_smooth(data5, mapping = aes(x = time, y = pm1)) + geom_smooth(data6, mapping = aes(x = time, y = pm1)) + geom_smooth(data7, mapping = aes(x = time, y = pm1)) + geom_smooth(data8, mapping = aes(x = time, y = pm1), color = "orange") 

```

**Description**

Thanks to this graph, we can compare air pollution in different cities in Armenia.

```{}
```

```{r}
#| message: false
#| echo: false

#| warning: false
#library(openair)
#data_new <- data_new[-c(4, 5, 15)]

#summaryPlot(data_new)
```

```{}
```

**Air pollution by month**

```{r}
#| message: false
#| echo: false

#| warning: false
data |>
  ggplot(data, mapping = aes(x = pm1, y = time)) + 
  geom_point(stat="identity", size=6) 
```

**Description**

This graph shows air pollution by month.

**The presence of pm1, pm2.5, pm10 in the air by months**

```{r}
#| message: false
#| echo: false

#| warning: false
data |>
  ggplot() + geom_point(mapping = aes(y = pm2_5, x = time, col="pm2,5", size="popdensity")) +  geom_point(mapping = aes(y = pm10, x = time, col="pm10")) + geom_point(mapping = aes(y = pm1, x = time, col="pm1")) +
  labs(x = "date", y = "pm1, pm2, pm2,5")
```

**Description**

This graph shows the number of pm1, pm2,5, pm10 in the air by month.



```{r}
#| message: false
#| echo: false

#| warning: false
data2 <-data
data2$year <- strftime(data_new$time, "%Y")
data2$month <- strftime(data_new$time, "%m")
data2$week <- strftime(data_new$time, "%w")
mydata <- data2
library(openair)
data("mydata")
summaryPlot(selectByDate(mydata))

```

