---
title: "website"
---



```{r}
library(tidyverse)
data <- read_csv("artik.csv")
library(openair)
library(lubridate)
library(ggplot2)
library(dplyr)
library(latticeExtra)

```

```{r}
data2 <- read_csv("sevan.csv")
data3 <- read_csv("ashotsk.csv")
data4 <- read_csv("azatan.csv")
data5 <- read_csv("gavar.csv")
data6 <- read_csv("maralik.csv")
data7 <- read_csv("panik.csv")
data8 <- read_csv("vazgen.csv")
data_new <- data
data_new$year <- strftime(data_new$time, "%Y")
data_new$month <- strftime(data_new$time, "%m")
data_new$week <- strftime(data_new$time, "%w")
data |>
  ggplot(mapping = aes(x = pm2_5, y = pm1)) + geom_point(aes(col="state", size="popdensity")) + geom_smooth(method="loess", se=F) 

ggplot() + geom_smooth(data_new, mapping = aes(x = time, y = temperature)) + geom_smooth(data2, mapping = aes(x = time, y = temperature)) + geom_smooth(data3, mapping = aes(x = time, y = temperature)) +geom_smooth(data4, mapping = aes(x = time, y = temperature)) + geom_smooth(data5, mapping = aes(x = time, y = temperature)) + geom_smooth(data6, mapping = aes(x = time, y = temperature)) + geom_smooth(data7, mapping = aes(x = time, y = temperature)) + geom_smooth(data8, mapping = aes(x = time, y = temperature), color = "orange")


ggplot() + geom_line(data_new, mapping = aes(x = time, y = pm1)) + geom_line(data2, mapping = aes(x = time, y = pm1)) + geom_line(data3, mapping = aes(x = time, y = pm1)) +geom_line(data4, mapping = aes(x = time, y = pm1)) + geom_line(data5, mapping = aes(x = time, y = pm1)) + geom_line(data6, mapping = aes(x = time, y = pm1)) + geom_line(data7, mapping = aes(x = time, y = pm1)) + geom_line(data8, mapping = aes(x = time, y = pm1), color = "orange")

timePlot(selectByDate(data_new, year = 2024, month = "may"),
         pollutant = c("pm2_5", "pm10"),
         y.relation = "free")

```

```{r}

data |>
  ggplot(data, mapping = aes(x = time, y=pm1)) + 
  geom_bar(stat="identity", fill="tomato3")

```

```{r}
data |>
  ggplot(data, mapping = aes(x = pm1, y = time)) + 
  geom_point(stat="identity", size=6) 
```





#data$date <- ymd_hms(data$time)
#data$year <- year(data$time)
#data$hour <- hour(data$time)
#data$month <- month(data$time)
#data$day <- day(data$time)
#data_daily <- timeAverage(data, avg.time = "day")
#head(data_daily)
#data_monthly <- timeAverage(data, avg.time = "month")
#head(data_monthly)
#data_yearly <- timeAverage(data, avg.time = "year")
#head(data_monthly)


#timePlot(selectByDate(data, year = 2024, month = "may"),
#         pollutant = c("pm2_5", "pm10", "ws"),
#y.relation = "free")





















